MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-10-10 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}

@@

roc roc roc
roc roc roc
roc roc roc

@@

roc roc roc
roc roc roc
roc roc roc

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{MLISA: Machine Learning-based \\ Intelligent Service Agents}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}
Now we evaluate the system specific results from user and community perspective. By distributing tasks among the communities over these time frames we evaluate the revenue for each community. Figure \ref{stats1} shows the overall revenue gain of communities using our method. Figure \ref{stats2} shows the momentarily gain of revenue for each community on each time slot compared to previous time. These results show how the run with higher learning rate of $r=0.20$ start discovering better communities to join much earlier. The runs with slow rate seems to find some communities to join initially, then slow down until later where they start discovering new communities to join with.

@@

@@

Figure \ref{stats3} depicts the average community size over time, which basically implies the number of new communities being formed. These results again show that the run with higher search rate tend to find appropriate communities to join faster.
